%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Development Engineer II} % Job title
    {Amazon} % Organization
    {Tennessee, USA} % Location
    {Mar. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, lead, coordinated, and implemented an annual rate structure change in the UK in 2 months to meet a hard deadline of February 14th. Organized changes to 11 different services, which were released in 18 different deployments to ensure system stability and rollback options. Coordinated these deployments with 4 different teams in 3 different timezones, involving over 10 SDEs and 4 PMs. These changes provided a 6.6\% revenue per package increase, unlocked an additional 1.5MM package volume with a projected 4.7MM additional revenue, and also reduced the time to make these changes in the future from 2 months to 2 weeks.}
        \item {Designed a solution to migrate our service from lambda compute to AWS Fargate. Mentored an intern and guided them to complete the project. Migration reduced time to deploy developmental changes by 50\%, and also eliminated cold starts from our application, allowing us to scale horizontally to meet increased traffic.}
        \item {Designed and implemented a data conversion and export pipeline to enable business report generation and KPI deep dives. Created a reusable CDK library implementation that is used by 4 different services.}
        \item {Coordinated and lead a design patterns Book club. Read book with 2 other engineers, and took turns leading a review session for each chapter with an average attendance of 5 people.}
        \item {Mentored 4 coworkers to help them get their first AWS certification. Lead a review meeting following a 6 week training to get the cloud practitioner certification with an average attendance of X.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {Amazon} % Organization
    {Tennessee, USA} % Location
    {Nov. 2019 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, created mockups, and implemented proof of concept UI that helped sales team negotiate rates with lead shippers, while also enforcing guardrails to protect profit margins}
        \item {Designed, lead, and implemented system expansion to support negotiations for all shippers, not just leads. Created tasks and estimates, owned delivery timeline, owned communication with stakeholders, and collaborated with coworkers to deliver on time and deprecate an excel based workflow.}
        \item {Organized multiple Nashville wide programming competitions (dubbed Codefest) with a peak of 27 participants, and an average satisfaction rating of 4.18 out of 5.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Harris Corporation} % Organization
    {Florida, USA} % Location
    {May 2018 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Interpreted customer requirements and designed class, component, and sequence diagrams to ensure system met customer needs. Defined and linked interfaces to model data and execution flow. ( MagicDraw )}
        \item {Mocked, designed, and implemented web interface. ( React, HTML, CSS, JavaScript )}
        \item {Designed and implemented backend services. ( Swagger, Node, Python )}
        \item {Created automated deployment and configuration of services and interfaces. ( Ansible, Make, RPMs, NGINX , AWS )}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
