%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Mentor} % Affiliation/role
    {Pivot Technology School} % Organization/group
    {Tennessee, USA} % Location
    {Aug. 2021 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Served as a mentor for one student attending a 16 week accelerated coding bootcamp targeted at closing the gap for minorities in tech.}
        \item {Assisted student with questions related to the curriculum, and provided examples on how classroom learning applies in the real world.}
        \item {Provided student insights into the world of tech, and provided help with and insight into the interview process.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Affiliation/role
    {Eve Profit} % Organization/group
    {USA} % Location
    {Jul. 2020 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designed and implemented a responsive website that helps Eve Online players find market information for in game items}
        \item {Designed and implemented a login system that allows users to see customized profit and return on investment}
        \item {Designed and implemented an automated image export processor that takes exported icons from the game and uploads them to a CDN so that they can be served on demand on the website}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Armchair IT Admin} % Affiliation/role
    {Home Lab} % Organization/group
    {USA} % Location
    {Oct. 2021 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Dell R210 II running PFSense as my firewall, OS installed on two mirrored SSDs using ZFS, connected to a Dell PowerConnect 7048 switch for VLAN support.}
        \item {Dell R720 running Proxmox as my hypervisor. TrueNAS core runs in a VM to manage my storage, with the raid controller (flashed to HBA mode) passed directly through via PCIE passthrough. VM storage made available VIA nfs running on TrueNAS.}
        \item {Highly available Pihole running as both a VM on the R720 and directly on a raspberry pi, kept in sync with Gravity sync. Automatic failover handled by a VIP managed by keepalived. DNS queries handled by unbound, running on the PFSense firewall.}
        \item {Other services running include Heimdall, Home Assistant, Portainer, Plex, and Guacamole.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
